\section{Conclusion}
\label{sec:conclusion}

We presented ConjLean and REFUTE, complementary systems for automated
mathematical conjecture generation, Lean~4 formalization, and multi-agent
counterexample refutation.
On a 92-conjecture benchmark, REFUTE with Qwen2.5-Math-7B achieves perfect
precision ($1.000$) and recall $0.292$ (E1), with all refutations attributable to
deterministic boundary sweep.
LLM-dependent strategies (symbolic perturbation, analogical transfer) do not
yet contribute at 7B scale.

Scaling from Qwen2.5-Math-7B to Qwen2.5-32B-Instruct (NF4 int4, E2) did not
change recall, precision, or the set of refuted conjectures.
Fixing a SymPy NL-parser bug that silently failed on $n^k$ expressions (E3)
raises recall from $0.292$ to $0.389$, recovering 7 additional Tier~1
number-theory conjectures.
Together, these results show that verifier correctness is a prerequisite for
meaningful recall measurement: bugs in the evaluation layer mask true pipeline
capability more than model scale affects it in the tested range.

Key lessons from E1, E2, and E3:
(1) zero false positives are achievable through exact SymPy integer arithmetic
--- but only when floating-point intermediates are avoided; a \texttt{float64}
truncation bug in the large-$n$ evaluation path produced two spurious
refutations in E3 before being identified and patched;
(2) recall for non-trivial strategies (SYMBOLIC\_PERTURBATION, ANALOGICAL)
did not improve across the tested scale and verifier-fix range, pointing to
LLM-generated candidate quality as the binding constraint;
(3) verifier and parser correctness matters more than model scale for recall
in the current regime.

\paragraph{Future work.}
Domain-specific LoRA fine-tuning of the Refuter on verified counterexample
triples (the \texttt{make finetune-refuter} pipeline) is the most direct path
to improving SYMBOLIC\_PERTURBATION yield.
Richer C-Agent prompting that explicitly checks whether refined statements
still fail at $n=1$ would address the refinement-loop failure mode identified
in \S\ref{sec:analysis}.
Extending the benchmark to cover algebraic geometry and combinatorial
identities would stress-test ANALOGICAL more meaningfully.
