\section{Related Work}
\label{sec:related}

\paragraph{Automated theorem proving.}
Lean-based interactive proof assistants~\citep{moura2021lean4} have been
combined with LLMs in systems such as
Draft-Sketch-Prove~\citep{jiang2023draft},
COPRA~\citep{TODO}, and
LeanDojo~\citep{yang2023leandojo}.
AlphaProof~\citep{alphageometry2024} demonstrates strong performance on
competition mathematics.
Our work is complementary: ConjLean focuses on \emph{refutation} and
conjecture generation rather than proof construction.

\paragraph{Counterexample search.}
Property-based testing~\citep{claessen2000quickcheck} is the dominant
approach in software verification but does not generalize naturally to
symbolic mathematical statements.
Nitpick~\citep{blanchette2010nitpick} and Sledgehammer~\citep{bohme2010sledgehammer} provide
counterexample search for Isabelle/HOL but are not LLM-augmented.
\citet{TODO} use LLMs to suggest falsifying inputs for program properties;
we adapt this idea to mathematical conjectures with symbolic verification.

\paragraph{Conjecture generation.}
FunSearch~\citep{romera2024funsearch} evolves programs that discover
mathematical structures but does not produce Lean-formalizable conjectures.
LLM-based conjecture generation has been explored in~\citet{TODO} without
a formal verification backend.
Ramanujan Machine~\citep{raayoni2021ramanujan} generates conjectures for
continued fractions via numerical pattern detection.

\paragraph{Multi-agent mathematical reasoning.}
Recent work on multi-agent LLM systems for mathematics~\citep{TODO} focuses
on collaborative proof construction.
Our S-Agent/R-Agent/C-Agent decomposition is, to our knowledge, the first
bandit-coordinated multi-strategy counterexample-search framework with
formal symbolic verification.
