\section{Results}
\label{sec:results}

\subsection{Primary Metrics}

Table~\ref{tab:main_results} reports overall REFUTE performance.
E1 (7B) achieves perfect precision with 21 refutations out of 92 conjectures.
Recall of $0.292$ means 51 of 72 truly-false conjectures are not refuted
by the 7B model on this benchmark.
E2 (32B int4) produces identical recall to E1: precision $1.000$, recall
$0.292$, F$_1$ $0.452$, all 21 refutations via BOUNDARY.
E3 (7B, patched verifier) improves recall to $0.389$: 28 correct refutations,
all via BOUNDARY, precision $1.000$.
The $+7$ refutations over E1 are exclusively in number theory and are entirely
attributable to the SymPy NL-parser fix described in \S\ref{sec:analysis}.

\begin{table}[h]
\centering
\caption{REFUTE primary metrics. CI = 95\% bootstrap confidence interval.
E3 figures exclude 2 RANDOM\_STRUCTURED false positives caused by a float64
precision bug (now fixed); see \S\ref{sec:analysis}.}
\label{tab:main_results}
\input{tables/main_results}
\end{table}

\subsection{Tier and Domain Breakdown}

Table~\ref{tab:breakdown} disaggregates results by tier and domain.
Several patterns are immediately apparent:

\begin{itemize}[noitemsep]
  \item \textbf{Number theory dominates.}
    All refutations across E1, E2, and E3 are in number theory.
    Inequality and combinatorics recall is $0.000$ in all three runs.

  \item \textbf{Tier 1 recall improves with the parser fix.}
    E1/E2 Tier~1 recall is $0.339$ (20/59).
    E3 raises this to $0.458$ (27/59), recovering
    7 additional Tier~1 conjectures involving $n^k$ expressions that
    previously failed to sympify.

  \item \textbf{Tier 2 / Tier 3 recall is unchanged.}
    Only 1 of 6 false Tier~2 conjectures is refuted in all three runs
    (the $n^2+1$ primality conjecture, refuted by $n=4$).
    Tier~3 recall is $0.000$, consistent with its design as a specificity test.
\end{itemize}

\begin{table}[h]
\centering
\caption{Tier and domain breakdown for E1, E2, and E3. Precision omitted where
$n_{\text{refuted}} = 0$.}
\label{tab:breakdown}
\input{tables/tier_domain_breakdown}
\end{table}

\subsection{Strategy Attribution}

Every E1 refutation was produced by the \textbf{BOUNDARY} strategy.
RANDOM\_STRUCTURED, SYMBOLIC\_PERTURBATION, and ANALOGICAL contributed zero
wins despite being exercised on all 71 survived conjectures (post-patch,
each received at least BOUNDARY + RANDOM\_STRUCTURED).
This finding motivated the 32B experiment: SYMBOLIC\_PERTURBATION and
ANALOGICAL are LLM-dependent and may require stronger generation capability
to produce verifiable candidates.
E2 (32B) confirms this pattern: all 21 refutations remain attributed to
BOUNDARY. Five survived conjectures received all four strategies (vs.\ at most
two in E1), yet none yielded a verified counterexample.
E3 continues this pattern: all 28 correct refutations are BOUNDARY wins.
RANDOM\_STRUCTURED produced two candidates that the pipeline initially
accepted, but both were subsequently identified as false positives caused
by a float64 precision bug in the SymPy evaluator (\texttt{int(\ldots.evalf())}
loses the last digits for $n \gtrsim 3{,}000$).
This bug has been fixed (\texttt{evalf()} removed from integer evaluation paths);
the two affected conjectures are also benchmark errors (universally true
by Fermat's little theorem) so they do not affect precision in context.
