\section{System Description}
\label{sec:system}

\subsection{ConjLean Pipeline}

ConjLean generates and formally verifies mathematical conjectures in four stages.

\paragraph{Stage 1: Conjecture generation.}
Given a domain (e.g., \texttt{number\_theory}), an LLM is prompted with
$k=20$ examples per batch at temperature $0.8$ to produce natural-language
conjectures involving a small number of integer variables.
Duplicate conjectures are filtered by normalized string hash.

\paragraph{Stage 2: SymPy symbolic pre-filter.}
Each conjecture is passed to a multiprocessing worker that attempts to
evaluate it symbolically via SymPy with a $5$-second SIGALRM timeout.
The filter adopts a \emph{conservative failure policy}: a conjecture is
rejected only when a confirmed counterexample is found; ambiguous or
timeout cases pass through.
This stage eliminates trivially false statements without LLM cost.

\paragraph{Stage 3: Lean 4 formalization.}
Surviving conjectures are translated to Lean~4 via an LLM with an error-repair
loop of up to five retries.
Each attempt is checked by a persistent Lean REPL subprocess communicating via
newline-delimited JSON.
Conjectures that fail to typecheck after five attempts are discarded.

\paragraph{Stage 4: Proof search.}
Formalized conjectures enter a four-layer proof search with escalating
timeouts: Layer~0 applies \texttt{auto} (5\,s); Layer~1 applies a library of
Mathlib tactic combinations (30\,s); Layer~2 applies search tactics including
\texttt{decide} and \texttt{norm\_num} (60\,s); Layer~3 engages a multi-turn
LLM dialogue to propose custom tactic sequences (120\,s, up to 3 rounds).

\subsection{REFUTE Pipeline}

REFUTE attacks conjectures that survive proof search (i.e., are neither proved
nor immediately disproved).
It coordinates three agents in a closed loop.

\paragraph{R-Agent (Refuter).}
Implements four counterexample-search strategies:
\begin{itemize}[noitemsep]
  \item \textbf{BOUNDARY}: deterministic sweep over edge cases
    ($n \in \{0, 1, 2, -1, \text{large primes}, \text{squares}, \ldots\}$).
    Cheap, requires no LLM.
  \item \textbf{RANDOM\_STRUCTURED}: samples candidates respecting variable
    constraints using prime/square/Fibonacci structure.
    Moderate cost, no LLM.
  \item \textbf{SYMBOLIC\_PERTURBATION}: prompts the LLM to identify parameter
    values that should stress-test the conjecture, then sweeps a neighborhood.
  \item \textbf{ANALOGICAL}: prompts the LLM to transfer counterexample
    patterns from past successes in the same domain.
\end{itemize}
Each candidate is verified by SymPy with a $4$-second async timeout.

\paragraph{S-Agent (Strategist).}
Selects which strategy to apply next using UCB1 with exploration constant
$C = \sqrt{2}$:
\[
  \text{score}(s) = \hat{w}(s) + C\sqrt{\frac{\ln N}{n_s}} + 0.2 \cdot \hat{w}_d(s)
\]
where $\hat{w}(s)$ is the empirical win rate of strategy $s$, $N$ is total
strategy attempts, $n_s$ is attempts of $s$, and $\hat{w}_d(s)$ is the
per-domain win rate (domain-awareness bonus).
When global sample counts are below $5$ per strategy, the Strategist falls
back to LLM guidance.
A low-confidence early-stop terminates a conjecture if all untried strategies
have $\geq 5$ global attempts with win rate $< 5\%$
\emph{and} at least two strategies have already been tried for the current
conjecture.

\paragraph{C-Agent (Conjecture Refiner).}
When a counterexample is confirmed, the C-Agent prompts the LLM to propose a
narrowed version of the conjecture that excludes the counterexample.
The loop restarts on the refined statement (up to three refinements).
If the LLM response cannot be parsed as JSON, a heuristic fallback appends an
exclusion clause.
